---
title: "Tutorial for WufooR"
author: "dmpe @ github"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

## Authentication

To access data from your surveys, you need to store your login information (name of subdomain and API key) in your local R environment. As described below, this can be done in two ways (ideas borrowed from [Scott Chamberlain](https://github.com/sckott) who used them in his `rnoaa` [package](https://github.com/ropensci/rnoaa/) package)

PS: Don't use my key, of course. See <https://wufoo.github.io/docs/>

> A helper function `auth_name()/auth_api()` looks for one of two stored keys, as an
environment variable under the name `Wufoo_Name`/`Wufoo_API`, or an option variable under the name
`Wufoo_Name`/`Wufoo_API`. 

> Environment variables can be set during session like `Sys.setenv(VAR = "...")`,
or stored long term in your `.Renviron` file. Option variables can be set during session
like `options(var = "...")`, or stored long term in your `.Rprofile` file.

```{r, eval=FALSE, include=T}
library(WufooR)

options(Wufoo_Name = "johnmalc", Wufoo_API = "put here your api key")
```

Print information about myself & API key.

```{r, eval=FALSE, include=T}
auth_name(NULL)
auth_key(NULL)
```

## User Information
 
Let's print some information about the user.

```{r, eval=FALSE, include=T}
t(user_info())
```

And now about the forms you have access to.

```{r, eval=FALSE, include=T}
t(form_info())

# Show responses to the form
fe_1 <- form_entries(formIdentifier = "z5kqx7h1gtvg4g")
t(fe_1)

sapply(fe_1, class)
```

And how many responses did we get sofar ?

```{r, eval=FALSE, include=T}
form_entriesCount(formIdentifier = "z5kqx7h1gtvg4g", domain = "wufoo.eu")
```

Show form's fields, with the requested URL (for debug purposes).

```{r, eval=FALSE, include=T}
fields_info(formIdentifier = "z5kqx7h1gtvg4g", showRequestURL = TRUE)
```

Do I have some reports ? If yes, then show me information about them.

```{r, eval=FALSE, include=T}
t(reports_info())
```

