---
title: "Tutorial for WufooR"
author: "dmpe @ github"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Authentication

You need to use store your login name (subdomain) and api key first. 

The methods used here has been written by [Scott Chamberlain](https://github.com/sckott), who wrote in the NEWS file of his `rnoaa` [package](https://github.com/ropensci/rnoaa/blob/master/NEWS):

> A new helper function `auth()` looks for one of two stored keys, as an
environment variable under the name `Wufoo_Name`, or an option variable under the name
`Wufoo_Name`. 

> Environment variables can be set during session like `Sys.setenv(VAR = "...")`,
or stored long term in your `.Renviron` file. Option variables can be set during session
like `options(var = "...")`, or stored long term in your `.Rprofile` file.

I kindly apply same code, slightly adapted.

```{r}
library(WufooR)

# options(Wufoo_Name = "YOUR_NAME")
options(Wufoo_Name = "johnmalc")

auth(NULL) # checks that it works
```


```{r}
user_info(ApiKey = "F1QH-Q64B-BSBI-JASJ")
```


```{r}
form_info(ApiKey = "F1QH-Q64B-BSBI-JASJ")

```


