---
title: "Tutorial for WufooR"
author: "dmpe @ github"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Authentication

To access data from your surways, you firstly need to store your login name (subdomain) and API Key. This can be done in two ways as described below. 

Initially, this has been written by [Scott Chamberlain](https://github.com/sckott), who wrote it in the NEWS file of his `rnoaa` [package](https://github.com/ropensci/rnoaa/blob/master/NEWS.md). I have addapted the names of my functions accordingly.

PS: Don't use my key, of course.

> A new helper function `auth_name()/auth_api()` looks for one of two stored keys, as an
environment variable under the name `Wufoo_Name`/`Wufoo_API`, or an option variable under the name
`Wufoo_Name`/`Wufoo_API`. 

> Environment variables can be set during session like `Sys.setenv(VAR = "...")`,
or stored long term in your `.Renviron` file. Option variables can be set during session
like `options(var = "...")`, or stored long term in your `.Rprofile` file.

```{r}
library(WufooR)

options(Wufoo_Name = "johnmalc", Wufoo_API = "F1QH-Q64B-BSBI-JASJ")
```

Print information about my name & api key.

```{r}
auth_name(NULL)
auth_key(NULL)
```

## Use Cases 
 
Let's print some information about the user.

```{r}
t(user_info())
```

And now about the forms you have access to.

```{r}
t(form_info())

# Show responses to the form
fe_1 <- form_entries(formIdentifier = "z5kqx7h1gtvg4g")
t(fe_1)

sapply(fe_1, class)
```

```{r}
# How many responses did you get ?
form_entriesCount(formIdentifier = "z5kqx7h1gtvg4g")
```

Show its fields, with the requested URL (for debug purposes).

```{r}
fields_info(formIdentifier = "z5kqx7h1gtvg4g", showRequestURL = TRUE)
```

Do you have some reports ? If yes, then show me information about them.

```{r}
t(reports_info())
```

