---
title: "Tutorial for WufooR"
author: "dmpe @ github"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial for WufooR}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

## Authentication

To access data from your surveys, you need to store your login information (name of `subdomain` and `API key`) in your local R environment. As described below, this can be done in two ways (this has been borrowed from [Scott Chamberlain](https://github.com/sckott)/his `rnoaa` [package](https://github.com/ropensci/rnoaa/) package).

PS: Don't use my `API key`, of course. See <https://wufoo.github.io/docs/>

> A helper function `auth_name()/auth_api()` looks for one of two stored keys, as an
environment variable under the name `Wufoo_Name`/`Wufoo_API`, or an option variable under the name
`Wufoo_Name`/`Wufoo_API`. 

> Environment variables can be set during session like `Sys.setenv(VAR = "...")`,
or stored long term in your `.Renviron` file. Option variables can be set during session
like `options(var = "...")`, or stored long term in your `.Rprofile` file.

```{r echo=FALSE}
library(WufooR)
# put here your api key
options(Wufoo_Name = "johnmalc", Wufoo_API = "S6VI-I8UA-BY11-TDHO")
```

Print information about myself & API key.

```{r, eval=FALSE, include=T}
auth_name(NULL)
auth_key(NULL)
```

## User Information
 
Let's print some information about the user.

```{r, eval=FALSE, include=T}
t(user_info())
```

And now what about the forms you have access to.

```{r, eval=FALSE, include=T}
t(form_info(formIdentifier = "z5kqx7h1gtvg4g", includeTodayCount="FALSE"))


t(form_info(includeTodayCount="FALSE"))

# Show responses to the form
fe_1 <- form_entries(formIdentifier = "z5kqx7h1gtvg4g")
t(fe_1)

sapply(fe_1, class)
```

And how many responses did we get sofar ?

```{r, eval=FALSE, include=T}
form_entriesCount(formIdentifier = "z5kqx7h1gtvg4g", domain = "wufoo.eu")
```

And form comments ?

```{r, eval=FALSE, include=T}
form_comments(formIdentifier = "z5kqx7h1gtvg4g", domain = "wufoo.eu")
form_commentsCount(formIdentifier = "z5kqx7h1gtvg4g")
```

Form entries in CSV ?

```{r, eval=FALSE, include=T}
form_entriesFromCSV(reportName = "untitled-report", showRequestURL = F)
```

Show form's fields, with the requested URL (for debug purposes).

```{r, eval=FALSE, include=T}
fields_info(formIdentifier = "z5kqx7h1gtvg4g", showRequestURL = FALSE)
```

## Report Information

Do I have some reports ? If yes, then show me information about them.

```{r, eval=FALSE, include=T}
# all reports
t(reports_info())

# only some reports
t(report_info(reportName = "untitled-report"))
```

Number of entries in the report and `details of the widgets that make up a specific report`.

```{r, eval=FALSE, include=T}
t(report_entries(reportName = "untitled-report"))

t(report_widgets(formIdentifier = "z5kqx7h1gtvg4g"))
```

